### 2016-06-06 Chapters/intro.tex
Minor changes in paper1

\section{Things}
On the continuous Galerkin paradigm, the need of an extra linear stabilization seems to be obvious and the challenge faced in \ref{chap-paper1} will be how to blend the linear and nonlinear stabilization in such a way that one preserves the DMP property. The discontinuous Galerkin, on the other hand, do already have implicit linear stabilization in its definition so the artificial viscosity can be directly applied on the top of it.

>>>>

\section{Things}
On the continuous Galerkin paradigm, the need of an extra linear stabilization seems to be obvious and the challenge faced in \ref{chap-paper1} will be how to blend the linear and nonlinear stabilization in such a way that one preserves the DMP property. The discontinuous Galerkin, on the other hand, do already have implicit linear stabilization in its definition so the artificial viscosity can be directly applied on the top of it.\\

The origin of continuous and discontinuous Galerkin. The amount of work related to the development of methods that enjoy the DMP for cG in comparison with dG. In this sense we feel that the present work is a remarkable contribution to the field since it includes methods that go from the analysis of the possible artificial diffusion techniques that would enjoy such properties to the implementation of graphviscosity methods that allow the method to stricly fulfil the property for any kind of underlying mesh.\\

In all of the cases a gradient jump viscosity shock detectors are implemented. The definition of those detectors can be generalized and applied either for continuous and discontinuous methods. This property is very interesting specially for hybrid meshes such as the continuous-discontinuous Galerkin method introduced in \cite{badia_adaptive_2013} for dealing with hanging nodes in adaptive meshes. In this sense, in chapter \ref{chap-paper3}, there is a possible approach to deal with the adaptive paradigm.\\

The present thesis aims to be the first compilation of different applications that take use of the Gradient Jump Viscosity shock detectors in order to implement Discrete Maximum Principle enjoying methods.\\

### 2016-06-06 Chapters/paper1.tex
Minor changes in paper1

The outline of the chapter is the following. In Section \ref{s-prel} we introduce the continuous problems and its
Galerkin discretization using FEs. Section \ref{s-fem} is devoted to the NPS formulation based on the Scott-Zhang projector and its corresponding numerical analysis. Section \ref{s-weightDMP} proposes a weighting of the previous linear stabilization in order to not affect the monotonicity of the underlying method. Novel nonlinear stabilization techniques are introduced in Section \ref{s-nonstab}. A summary of the linear/nonlinear schemes used in the numerical experimentation, including the ones proposed in this work, can be found in Algorithm \ref{alg-wNPS-GJV}. Numerical experiments are included in Section \ref{s-numex}. Finally, some conclusions are drawn in Section \ref{s-concl}.

@@

In this work, we extend the NPS method (recently proposed in \cite{badia_stabilized_2012} to attain pressure stability for the Stokes problem) to convection stabilization. We consider $\kappa_h$ to be a particular $L^1(\Omega)$ Scott-Zhang projector, which is favoured with respect to the previous symmetric stabilization techniques since \emph{only local projections} are required and neither \emph{assumptions over the mesh partition} nor \emph{enriched FE spaces} are needed. We note that the projector is locally defined at the node level, which has motivated the name of the method.

@@

Finally, we prove error estimates for this algorithm. We remark that linear projection stabilization methods are weakly consistent, i.e., the consistency error does not spoil the overall convergence rates, as soon as the projector $\kappa_h$ in \Eq{projSZ} has optimal approximation properties, i.e., for any $v\in W^l_p(\Omega)$ and $0\leq s \leq l \leq k+1$, it holds:
\begin{align}\label{eq-orthapprox}
\|\kappa_h^\perp(v)\|_{W^s_p(K)} \lesssim h^{l-s} \|v\|_{W^l_p(S_K)}, \qquad 
\|\kappa_h^\perp(v)\|_{W^s_p(\Omega)} \lesssim h^{l-s} \|v\|_{W_p^l(\Omega)},
\end{align}
where $S_K$ is a domain made of the elements neighboing $K$ (see \cite{brenner_mathematical_2010}).  We consider first the analysis for the  symmetric stabilization \Eq{stproj1}.
\begin{theorem}[Convergence]\label{th:conv}
Let $u_h \in V_h^k$ be the solution of \Eq{SZstab} with the linear stabilization term $s_h(\cdot,\cdot)$ defined in  \Eq{stproj1}  and the projector $\kappa_h(\cdot)$ defined in \Eq{projSZ}. Let us assume that the solution $u$ of \Eq{probcont} belongs to $L^\infty(0,T;H^l(\Omega))$ for $l \leq k+1$, and $\beta\in L^\infty(0,T;W^{1,\infty}(\Omega))$. The following error estimate holds for any $t^* \in (0,T)$:
\begin{align*}
& \|(u_h-u)(t^*)\| + \| \delta^\frac{1}{2} \bb \cdot \szpp \nabla  (u_h-u) \|_{L^2(\Qq)}   \\
%& \|(u_h-u)(t^*)\| + \|s_h(u_h-u,u_h-u)\|_{L^2(0,t^*)}   \\
%& \qquad \lesssim   h^{l} \|u(t^*)\|_{H^l(\Omega)}  +  h^{l-\half}\|\bb\|_{L^{\infty}(\Omega)}^\half \|u\|_{L^2(0,t^*;H^l(\Omega))} \left( 1 +  \exp\left( h t^* \|\bb\|_{W^{1,\infty}(Q)}^2\right)\right),
& \qquad \lesssim 
  h^{l} \|u(t^*)\|_{H^l(\Omega)}  +  h^{l-\half}\|\bb\|_{L^{\infty}(\Qq)}^\half \|u\|_{L^2(0,t^*;H^l(\Omega))} \left( 1 + e^{t^* {\bar \delta } \|\bb  \|^2_{L^\infty(0,t^*;W^{1,\infty}(\Omega))}}
% \exp\left( t^* \left\|{\bar \delta {\|\bb\|_{W^{1,\infty}(\Omega)}^2}}\right\|_{L^\infty(0,t^*)}\right)
\right). 
\end{align*}
\end{theorem}

@@

& \|\xi(t^*)\|^2  + \sno{\xi}  +\tint{c_s(\xi,\xi)} \cl &=  - \tint{s_h(u,\xi)} + \tint{(\partial_t \eta, \xi)} + \tint{(\bb\cdot \nabla \eta,\xi)} + \tint{s_h(\eta,\xi)}  =  I + II + III + IV,

@@

& \  \leq \tint{\frac{\alpha}{2} \frac{\|\bb\|_{L^\infty(\Omega)}}{h} \|\eta\|^2} + \tint{\frac{1}{2\alpha} \| \bar \delta^\half \lpp(\bb \cdot \nabla \xi)\|^2} +\tint{\left(\theta \|\beta\|_{L^\infty(\Omega)}\|\eta\|\|\nabla \eta\| + \frac{1}{\theta}c_s(\xi,\xi)\right)},

@@

+ \tint{\frac{\bar \delta}{\alpha} \| \bb \cdot \szpp (\nabla  \xi) \|^2 }
+ \tint{ \frac{\bar \delta}{\alpha}  {\|\bb\|_{W^{1,\infty}(\Omega)}^2}  \|\xi\|^2} + \\\
& + \theta h^{2l-1} \|\bb\|_{L^\infty(\Qq)}  \|u\|^2_{L^2(0,t^*;H^l(\Omega))} + \frac{1}{\theta} \tint{c_s(\xi,\xi)}  .

@@

\|\xi(t^*)\|^2 + \sno{\xi}  \lesssim  h^{2l-1}\|\bb\|_{L^\infty(\Qq)} \|u\|_{L^2(0,t^*;H^l(\Omega))}^2 +  \tint { \bar \delta \|\bb\|_{W^{1,\infty}(\Omega)}^2 \|\xi\|^2}.

@@

\|\xi(t^*)\|^2 + \sno{\xi} \lesssim  h^{2l-1}\|\bb\|_{L^\infty(\Qq)} \|u\|_{L^2(0,t^*;H^l(\Omega))}^2 e^{t^* {\bar \delta } \|\bb  \|^2_{L^\infty(0,t^*;W^{1,\infty}(\Omega))}}.

@@

\|\eta(t^*)\|^2 + \sno{\eta} \lesssim h^{2l} \|u(t^*)\|_{H^l(\Omega)}^2 + h^{2l-1}\|\bb\|_{L^\infty(\Qq)} \|u\|^2_{L^2(0,t^*;H^l(\Omega))}.

>>>>

The outline of the chapter is the following. In Section \ref{s-prel} we introduce the continuous problems and its
Galerkin discretization using FEs. Section \ref{s-fem} is devoted to the NPS formulation based on the Scott-Zhang projector and its corresponding numerical analysis. Section \ref{s-weightDMP} proposes a weighting of the previous linear stabilization in order to not affect the monotonicity of the underlying method. Novel nonlinear stabilization techniques are introduced in Section \ref{s-nonstab}. A summary of the linear/nonlinear schemes used in the numerical experimentation, including the ones introduced in this chapter, can be found in Algorithm \ref{alg-wNPS-GJV}. Numerical experiments are included in Section \ref{s-numex}. Finally, some conclusions are drawn in Section \ref{s-concl}.

@@

We will extend the NPS method (recently proposed in \cite{badia_stabilized_2012} to attain pressure stability for the Stokes problem) to convection stabilization. We consider $\kappa_h$ to be a particular $L^1(\Omega)$ Scott-Zhang projector, which is favoured with respect to the previous symmetric stabilization techniques since \emph{only local projections} are required and neither \emph{assumptions over the mesh partition} nor \emph{enriched FE spaces} are needed. We note that the projector is locally defined at the node level, which has motivated the name of the method.

@@

Finally, we prove error estimates for this algorithm. We remark that linear projection stabilization methods are weakly consistent, i.e., the consistency error does not spoil the overall convergence rates, as soon as the projector $\kappa_h$ in \Eq{projSZ} has optimal approximation properties, i.e., for any $v\in W^{l,p}(\Omega)$ and $0\leq s \leq l \leq k+1$, it holds:
\begin{align}\label{eq-orthapprox}
\|\kappa_h^\perp(v)\|_{W^{s,p}(K)} \lesssim h^{l-s} \|v\|_{W^{l,p}(S_K)}, \qquad 
\|\kappa_h^\perp(v)\|_{W^{s,p}(\Omega)} \lesssim h^{l-s} \|v\|_{W^{l,p}(\Omega)},
\end{align}
where $S_K$ is a domain made of the elements neighboring $K$ (see \cite{brenner_mathematical_2010}).  We consider first the analysis for the  symmetric stabilization \Eq{stproj1}.
\begin{theorem}[Convergence]\label{th:conv}
Let $u_h \in V_h^k$ be the solution of \Eq{SZstab} with the linear stabilization term $s_h(\cdot,\cdot)$ defined in  \Eq{stproj1}  and the projector $\kappa_h(\cdot)$ defined in \Eq{projSZ}. Let us assume that the solution $u$ of \Eq{probcont} belongs to $L^\infty(0,T;H^l(\Omega))$ for $l \leq k+1$, and $\beta\in L^\infty(0,T;W^{1,\infty}(\Omega))$. The following error estimate holds for any $t^* \in (0,T)$:
\begin{align*}
& \|(u_h-u)(t^*)\| + \| \delta^\frac{1}{2} \bb \cdot \szpp \nabla  (u_h-u) \|_{L^2(\Qq)}   \\
%& \|(u_h-u)(t^*)\| + \|s_h(u_h-u,u_h-u)\|_{L^2(0,t^*)}   \\
%& \qquad \lesssim   h^{l} \|u(t^*)\|_{H^l(\Omega)}  +  h^{l-\half}\|\bb\|_{L^{\infty}(\Omega)}^\half \|u\|_{L^2(0,t^*;H^l(\Omega))} \left( 1 +  \exp\left( h t^* \|\bb\|_{W^{1,\infty}(Q)}^2\right)\right),
& \qquad \lesssim 
  h^{l} \|u(t^*)\|_{H^l(\Omega)}  +  h^{l-\half}\|\bb\|_{L^{\infty}(\Qq)}^\half \|u\|_{L^2(0,t^*;H^l(\Omega))} \left( 1 + e^{t^* {\bar \delta } \|\bb  \|^2_{L^\infty(0,t^*;W^{1,\infty}(\Omega))}}
% \exp\left( t^* \left\|{\bar \delta {\|\bb\|_{W^{1,\infty}(\Omega)}^2}}\right\|_{L^\infty(0,t^*)}\right)
\right). 
\end{align*}
\end{theorem}

@@

 \|&\xi(t^*)\|^2  + \sno{\xi}  +\tint{c_s(\xi,\xi)} \cl &=  - \tint{s_h(u,\xi)} + \tint{(\partial_t \eta, \xi)} + \tint{(\bb\cdot \nabla \eta,\xi)} + \tint{s_h(\eta,\xi)} \cl & =  I + II + III + IV,

@@

& \  \leq \tint{\frac{\alpha}{2} \frac{\|\bb\|_{L^\infty(\Omega)}}{h} \|\eta\|^2} + \tint{\frac{1}{2\alpha} \| \bar \delta^\half \lpp(\bb \cdot \nabla \xi)\|^2} \\
& +\tint{\left(\theta \|\beta\|_{L^\infty(\Omega)}\|\eta\|\|\nabla \eta\| + \frac{1}{\theta}c_s(\xi,\xi)\right)},

@@

+ \tint{\frac{\bar \delta}{\alpha} \| \bb \cdot \szpp (\nabla  \xi) \|^2 }\\
& + \tint{ \frac{\bar \delta}{\alpha}  {\|\bb\|_{W^{1,\infty}(\Omega)}^2}  \|\xi\|^2} + \theta h^{2l-1} \|\bb\|_{L^\infty(\Qq)}  \|u\|^2_{L^2(0,t^*;H^l(\Omega))}\\
& + \frac{1}{\theta} \tint{c_s(\xi,\xi)}  .

@@

\|&\xi(t^*)\|^2 + \sno{\xi}  \lesssim  h^{2l-1}\|\bb\|_{L^\infty(\Qq)} \|u\|_{L^2(0,t^*;H^l(\Omega))}^2 \\
& +  \tint { \bar \delta \|\bb\|_{W^{1,\infty}(\Omega)}^2 \|\xi\|^2}.

@@

\|&\xi(t^*)\|^2 + \sno{\xi} \\
& \lesssim  h^{2l-1}\|\bb\|_{L^\infty(\Qq)} \|u\|_{L^2(0,t^*;H^l(\Omega))}^2 e^{t^* {\bar \delta } \|\bb  \|^2_{L^\infty(0,t^*;W^{1,\infty}(\Omega))}}.

@@

\|&\eta(t^*)\|^2 + \sno{\eta} \\
& \lesssim h^{2l} \|u(t^*)\|_{H^l(\Omega)}^2 + h^{2l-1}\|\bb\|_{L^\infty(\Qq)} \|u\|^2_{L^2(0,t^*;H^l(\Omega))}.

### 2016-06-06 symbols_definition.tex
Minor changes in paper1

\multicolumn{3}{c}{{\Large \textbf{Upper-case Roman}}} \\
$\mathcal{N}_h(K)$ & Set of interpolation nodes & \\
$\thn$ & finite element mesh & \\
$\thm$ & finite element adaptive mesh at adaptivity step $m$ &\\	
$\vh$ & piecewise polynomial space of discrete solutions (continuous or discontinuous)& \\
$V_h^k$ & piecewise polynomial space of order $k$  &\\
$V_{h,0}$ & piecewise polynomial space with homogeneous Dirichlet boundary conditions  &\\
$\vm$ & piecewise polynomial space of discrete solutions at the $m$ adaptive step & \\

\multicolumn{3}{c}{{\Large \textbf{Lower-case Greek}}} \\
$\beta$ & convection term& \\
$ \tau_c $ & continuity stabilization parameter & \\

>>>>

\multicolumn{3}{c}{{\Large \textbf{Upper-case Roman}}} \\
$\facet$ & facet & \\
$H^\beta(\Omega)$ & Space of solutions of the weak transport problem &\\
& { ($H^\beta(\Omega) := \{ u \in L^2(\Omega): \,  \nabla \cdot (\beta u) \in L^2(\Omega) \}$)}\\
$K$, $K_i$ & elements of the mesh (in Chaper \ref{chap-paper3} they are ordered by convenience of the analysis) & \\
$K^+_\facet$/$K^-_\facet$ & elements that surround facet $\facet$ ($\facet = \partial K^+_\facet\cap K^-_\facet$ ) & \\
$\mathcal{N}_h(K)$ & Set of interpolation nodes & \\
$P_k(\omega)$ & space of complete polynomials of degree $k$ on $\omega$ & \\
$Q_k(\omega)$ & space of polynomials with maximum degree $k$ in $\omega$\\
$\thn$ & finite element mesh & \\
$\thm$ & finite element adaptive mesh at adaptivity step $m$ &\\	
$\vh$ & piecewise polynomial space of discrete solutions (continuous or discontinuous)& \\
$V_h^k$ & piecewise polynomial space of order $k$  &\\
$V_{h,0}$ & piecewise polynomial space with homogeneous Dirichlet boundary conditions  &\\
$\vm$ & piecewise polynomial space of discrete solutions at the $m$ adaptive step & \\
$W^{l,p}$ & Sobolev space & \\
\addlinespace % Gap to separate the Roman lower from Roman Capital
\addlinespace

\multicolumn{3}{c}{{\Large \textbf{Lower-case Greek}}} \\
$\beta$ & convection term& \\
$\kappa_h$ & Scott-Zhang projector & \\
$\varsigma$ & node-to-element map & \\
$ \tau_c $ & continuity stabilization parameter & \\
